Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
Intro to results

\section{Results} \label{results}
Introduction.

%%Intoduce the four sections added, removed, modified & general trends.

\subsection{RQ1 Results}

@@

\subsection{RQ2 Results}
The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.

>>>>

\section{Results} \label{results}
This section will present the results of our study. The results related to \textbf{RQ1} and \textbf{RQ1.1} are introduced in Section \ref{results_rq1}, and the results of \textbf{RQ2} are presented in Section \ref{results_rq2}

\subsection{RQ1 Results} \label{results_rq1}

@@

\subsection{RQ2 Results} \label{results_rq2}
The results related to \textbf{RQ2} are structured around each of Lehman's laws and to what extent our findings show that the laws apply to platform APIs. A summary of our findings can be seen in Table \ref{table:lehman}.
